Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-18 presentation.qmd
add val css, and more val plots

## What are your chances of winning a round, given the series state in COD SnD?

@@

## What are your chances of winning a round, given the series state in COD SnD?

```{r}
#| label: p_cod_o_round_win_prop_over_expected
heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f\n(%s)', 
    100 * .df[[.label]], 
    scales::comma(.df$n)
  )
}

@@

cod_max_diff_win_round_prop <- max(abs(cod_o_win_prop$diff_win_round_prop))
p_cod_o_round_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'diff_win_round_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_round_win_over_expected_text_layer,
    .threshold = -0.1,
    .labeller = heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_round_prop, 
      +cod_max_diff_win_round_prop
    )
  ) +
  labs(
    title = 'Offensive Round Win % Over Expected'
  )
p_cod_o_round_win_prop_over_expected
save_for_slide(p_cod_o_round_win_prop_over_expected)
```

@@

## What are your chances of winning a round, given the series state in Valorant?

@@

@@

filt_val_o_win_prop <- val_o_win_prop |> 
  filter(pre_cumu_w <= 12, pre_cumu_l <= 12)

val_pre_swap_rounds <- filt_val_o_win_prop |> 
  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
  filter(pre_cumu_wl == 12)

@@

p_val_o_round_win_prop <- filt_val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = filt_val_o_win_prop, 
    .f = o_round_win_text_layer,
    .num = NULL,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_val_o_round_win_prop
save_for_slide(p_val_o_round_win_prop)
```

@@

## What are your chances of winning the series, given the series state?

@@

cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
p_cod_o_series_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.08,
    .labeller = heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_series_prop, 
      +cod_max_diff_win_series_prop
    )
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_cod_o_series_win_prop_over_expected
save_for_slide(p_cod_o_series_win_prop_over_expected)
```

@@

>>>>

## What are your chances of winning a round, given the series state in [COD SnD]{.cod}?

@@

## What are your chances of winning a round, given the series state in [COD SnD]{.cod}?

```{r}
#| label: p_cod_o_round_win_prop_over_expected
cod_heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f\n(%s)', 
    100 * .df[[.label]], 
    scales::comma(.df$n)
  )
}

@@

cod_max_diff_win_round_prop <- max(abs(cod_o_win_prop$diff_win_round_prop))
p_cod_o_round_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(.fill = 'diff_win_round_prop') +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_round_win_over_expected_text_layer,
    .threshold = -0.1,
    .labeller = cod_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('purple'),
    high = extract_ggsci_mid_color('green'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_round_prop, 
      +cod_max_diff_win_round_prop
    )
  ) +
  labs(
    title = 'Offensive Round Win % Over Expected'
  )
p_cod_o_round_win_prop_over_expected
save_for_slide(p_cod_o_round_win_prop_over_expected)
```

@@

## What are your chances of winning a round, given the series state in [Valorant]{.valorant}?

@@

drop_25th_round <- function(df) {
  df |> 
    filter(
      !(pre_cumu_w == 12 & pre_cumu_l == 12)
    )
}

val_e_o_win_series_prop <- crossing(
  pre_cumu_w = 0:12,
  pre_cumu_l = 0:12
) |> 
  drop_25th_round() |> 
  mutate(
    n_remain_max = 25 - (pre_cumu_w + pre_cumu_l),
    n_remain_w = 13 - pre_cumu_w,
    ## can i account for offense in this by rotating?
    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
  )

val_o_win_prop <- val_o_win_prop |> 
  inner_join(
    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
    by = c('pre_cumu_w', 'pre_cumu_l')
  ) |> 
  mutate(
    diff_win_series_prop = win_series_prop - e_win_series_prop
  ) |> 
  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
  drop_25th_round()

@@

val_pre_swap_rounds <- val_o_win_prop |> 
  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
  filter(pre_cumu_wl == 12)

@@

p_val_o_round_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_round_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_round_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('teal') +
  labs(
    title = 'Offensive Round Win %'
  )
p_val_o_round_win_prop
save_for_slide(p_val_o_round_win_prop)
```

@@

## What are your chances of winning the series, given the series state in [COD SnD]{.cod}?

@@

cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
p_cod_o_series_win_prop_over_expected <- cod_o_win_prop |> 
  ggplot() +
  common_cod_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = cod_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.08,
    .labeller = cod_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    midpoint = 0,
    limits = c(
      -cod_max_diff_win_series_prop, 
      +cod_max_diff_win_series_prop
    )
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_cod_o_series_win_prop_over_expected
save_for_slide(p_cod_o_series_win_prop_over_expected)
```

@@

## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?

```{r}
#| label: p_val_o_series_win_prop
p_val_o_series_win_prop <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(.fill = 'win_series_prop') +
  geom_path(
    data = val_pre_swap_round_segments,
    color = 'white',
    size = 1.5,
    aes(
      x = pre_cumu_w, 
      y = pre_cumu_l
    )
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_text_layer,
    .threshold = 0.8,
    .labeller = val_heatmap_seq_labeller
  ) +
  ggsci::scale_fill_material('orange') +
  labs(
    title = 'Offensive Series Win %'
  )
p_val_o_series_win_prop
save_for_slide(p_val_o_series_win_prop)
```

![](val_o_series_win_prop.png){fig-align="center"}

## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?

```{r}
#| label: p_val_o_series_win_prop_over_expected
val_heatmap_div_labeller <- function(.df, .label, .num) {
  sprintf(
    '%+.1f', 
    100 * .df[[.label]]
  )
}

val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
p_val_o_series_win_prop_over_expected <- val_o_win_prop |> 
  ggplot() +
  common_val_heatmap_layers() +
  heatmap_tile(
    .fill = 'diff_win_series_prop'
  ) +
  heatmap_text_layers(
    .df = val_o_win_prop, 
    .f = o_series_win_over_expected_text_layer,
    .threshold = 0.2,
    .labeller = val_heatmap_div_labeller
  ) +
  scale_fill_gradient2(
    low = extract_ggsci_mid_color('brown'),
    high = extract_ggsci_mid_color('cyan'),
    mid = 'white',
    limits = c(
      -val_max_diff_win_series_prop,
      +val_max_diff_win_series_prop
    ),
    midpoint = 0
  ) +
  labs(
    title = 'Offensive Series Win % Over Expected'
  )
p_val_o_series_win_prop_over_expected
save_for_slide(p_val_o_series_win_prop_over_expected)
```

![](val_o_series_win_prop_over_expected.png){fig-align="center"}
